# Parameter recovery Yearsley (Y-RL)

# Load packages and functions
```{r}
# Load packages
pacman::p_load(ggplot2, tidyverse, RColorBrewer, brms)
options(dplyr.summarise.inform = FALSE)

# Set to source file location 
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
source("../../utils/quality_check_functions.R")
```

# Load data
```{r}
# Reset and specify model
fit_all = NULL
sim_data = "yearsley"

# Load data saved in csv
fit_all <- read_csv(paste0("output/", sim_data, "/fit_all.csv"))

# Load data anew
param_combination = readRDS(paste0("../fitting/output/sim_", sim_data, "/param_combination.rds"))

for (i in 1:nrow(param_combination[param_combination$n_agent == 1,])){ # loading for n_agent = 1
 
  fit = as.data.frame(readRDS(paste0("../fitting/output/sim_", sim_data, "/model_yearsley/fit_", i, ".rds")))
  fit$model = "yearsley"
  
  fit = fit[,1:15] # subset relevant columns
  fit$id = i
  fit$n_agent = param_combination$n_agent[i]
  fit$true_alpha_pos_p =  param_combination$alpha_pos[i]
  fit$true_alpha_neg_p = param_combination$alpha_neg[i]
  fit$true_f_p = param_combination$f[i]
  fit$true_alpha_pos_log = brms::logit_scaled(param_combination$alpha_pos[i])
  fit$true_alpha_neg_log = brms::logit_scaled(param_combination$alpha_neg[i])
  fit$true_f_log = brms::logit_scaled(param_combination$f[i])
  
  if (exists("fit_all")) {fit_all = rbind(fit_all, fit)} 
  else {fit_all = fit}

}

# Save csv
write_csv(fit_all, "output/yearsley/fit_all.csv")

# Summarise data
fit_summary = fit_all %>% 
    group_by(id, true_f_p, true_alpha_pos_p, true_alpha_neg_p) %>% 
    summarise(true_alpha_pos_log = mean(true_alpha_pos_log),
              true_alpha_neg_log = mean(true_alpha_neg_log),
              true_f_log = mean(true_f_log),
              alpha_pos_posterior_log = mean(alpha_pos_posterior_log),
              alpha_pos_posterior_p = mean(alpha_pos_posterior_p),
              alpha_neg_posterior_log = mean(alpha_neg_posterior_log),
              alpha_neg_posterior_p = mean(alpha_neg_posterior_p),
              f_posterior_log = mean(f_posterior_log),
              f_posterior_p = mean(f_posterior_p))

# Round values
fit_round <- data.frame(lapply(fit_summary, function(x) if(is.numeric(x)) round(x, 2) else x))
```


### Visualisations
To change between plots on the probability scale and the log-odds scale when relevant, change the subscript of the given variable between _p and _log.

## Overall plots for each parameter in the model
```{r}
# Alpha_r
recovery_overall(fit_round, "true_alpha_pos_p", "alpha_pos_posterior_p", "Alpha_r", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/overall_alpha_r.png"), width = 4.2, height = 5)
# Alpha_p
recovery_overall(fit_round, "true_alpha_neg_p", "alpha_neg_posterior_p", "Alpha_p", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/overall_alpha_p.png"), width = 4.2, height = 5)
# Phi
recovery_overall(fit_round, "true_f_p", "f_posterior_p", "Phi", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/overall_phi.png"), width = 4.2, height = 5)
```

## Interactions

# Recovering alpha_r
```{r}
# Over alpha_p
recovery_over_var_3(fit_round, "true_alpha_pos_p", "alpha_pos_posterior_p", "true_alpha_neg_p", "Alpha_p", "Alpha_r", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/alpha_r_alpha_p.png"), width = 4.2, height = 5)
# Over phi
recovery_over_var_3(fit_round, "true_alpha_pos_p", "alpha_pos_posterior_p", "true_f_p", "Phi", "Alpha_r", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/alpha_r_phi.png"), width = 4.2, height = 5)
```

# Recovering alpha_p
```{r}
# Over alpha_r
recovery_over_var_3(fit_round, "true_alpha_neg_p", "alpha_neg_posterior_p", "true_alpha_pos_p", "Alpha_r", "Alpha_p", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/alpha_p_alpha_r.png"), width = 4.2, height = 5)
# Over phi
recovery_over_var_3(fit_round, "true_alpha_neg_p", "alpha_neg_posterior_p", "true_f_p", "Phi", "Alpha_p", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/alpha_p_phi.png"), width = 4.2, height = 5)
```

# Recovering phi
```{r}
# Over alpha_r
recovery_over_var_3(fit_round, "true_f_p", "f_posterior_p", "true_alpha_pos_p", "Alpha_r", "Phi", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/phi_alpha_r.png"), width = 4.2, height = 5)
# Over alpha_p
recovery_over_var_3(fit_round, "true_f_p", "f_posterior_p", "true_alpha_neg_p", "Alpha_p", "Phi", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/phi_alpha_p.png"), width = 4.2, height = 5)
```


### Correlations
Allows us to get the correlations as part of the "residual correlations"

## Overall correlations
```{r}
# Formulas
f_alpha_pos <- bf(mvbind(true_alpha_pos_p, alpha_pos_posterior_p) ~ 1) + set_rescor(TRUE)
f_alpha_neg <- bf(mvbind(true_alpha_neg_p, alpha_neg_posterior_p) ~ 1) + set_rescor(TRUE)
f_f <- bf(mvbind(true_f_p, f_posterior_p) ~ 1) + set_rescor(TRUE)

# Run models
alpha_pos_cor <- brm(
  formula = f_alpha_pos,
  data = fit_summary,
  family = gaussian,
  chains = 4,
  cores = 4,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 20),
  seed = 1)

alpha_neg_cor <- brm(
  formula = f_alpha_neg,
  data = fit_summary,
  family = gaussian,
  chains = 4,
  cores = 4,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 20),
  seed = 1)

f_cor <- brm(
  formula = f_f,
  data = fit_summary,
  family = gaussian,
  chains = 4,
  cores = 4,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 20),
  seed = 1)

# Summary
summary(alpha_pos_cor)
summary(alpha_neg_cor)
summary(f_cor)

# Get parameter/variable names
variables(alpha_pos_cor)
variables(alpha_neg_cor)
variables(f_cor)

# Test hypotheses
hypothesis(alpha_pos_cor, "rescor__truealphaposp__alphaposposteriorp > 0.5", class = NULL)
hypothesis(alpha_neg_cor, "rescor__truealphanegp__alphanegposteriorp > 0.5", class = NULL)
hypothesis(f_cor, "rescor__truefp__fposteriorp > 0.5", class = NULL)
```

## Interactions

# Alpha_r
```{r}
# Update data for interactions
# Over alpha_p
alpha_r_alpha_p_01 <- update(alpha_pos_cor, newdata = fit_summary[fit_summary$true_alpha_neg_p == 0.1, ], seed = 1)
alpha_r_alpha_p_03 <- update(alpha_pos_cor, newdata = fit_summary[fit_summary$true_alpha_neg_p == 0.3, ], seed = 1)
alpha_r_alpha_p_05 <- update(alpha_pos_cor, newdata = fit_summary[fit_summary$true_alpha_neg_p == 0.5, ], seed = 1)
alpha_r_alpha_p_07 <- update(alpha_pos_cor, newdata = fit_summary[fit_summary$true_alpha_neg_p == 0.7, ], seed = 1)
alpha_r_alpha_p_09 <- update(alpha_pos_cor, newdata = fit_summary[fit_summary$true_alpha_neg_p == 0.9, ], seed = 1)
# Over phi
alpha_r_phi_01 <- update(alpha_pos_cor, newdata = fit_summary[fit_summary$true_f_p == 0.1, ], seed = 1)
alpha_r_phi_03 <- update(alpha_pos_cor, newdata = fit_summary[fit_summary$true_f_p == 0.3, ], seed = 1)
alpha_r_phi_05 <- update(alpha_pos_cor, newdata = fit_summary[fit_summary$true_f_p == 0.5, ], seed = 1)
alpha_r_phi_07 <- update(alpha_pos_cor, newdata = fit_summary[fit_summary$true_f_p == 0.7, ], seed = 1)
alpha_r_phi_09 <- update(alpha_pos_cor, newdata = fit_summary[fit_summary$true_f_p == 0.9, ], seed = 1)


# Summary
# Over alpha_p
summary(alpha_r_alpha_p_01)
summary(alpha_r_alpha_p_03)
summary(alpha_r_alpha_p_05)
summary(alpha_r_alpha_p_07)
summary(alpha_r_alpha_p_09)
# Over phi
summary(alpha_r_phi_01)
summary(alpha_r_phi_03)
summary(alpha_r_phi_05)
summary(alpha_r_phi_07)
summary(alpha_r_phi_09)


# Test hypotheses
# Over alpha_p
hypothesis(alpha_r_alpha_p_01, "rescor__truealphaposp__alphaposposteriorp > 0.5", class = NULL)
hypothesis(alpha_r_alpha_p_03, "rescor__truealphaposp__alphaposposteriorp > 0.5", class = NULL)
hypothesis(alpha_r_alpha_p_05, "rescor__truealphaposp__alphaposposteriorp > 0.5", class = NULL)
hypothesis(alpha_r_alpha_p_07, "rescor__truealphaposp__alphaposposteriorp > 0.5", class = NULL)
hypothesis(alpha_r_alpha_p_09, "rescor__truealphaposp__alphaposposteriorp > 0.5", class = NULL)

# Over phi
hypothesis(alpha_r_phi_01, "rescor__truealphaposp__alphaposposteriorp > 0.5", class = NULL)
hypothesis(alpha_r_phi_03, "rescor__truealphaposp__alphaposposteriorp > 0.5", class = NULL)
hypothesis(alpha_r_phi_05, "rescor__truealphaposp__alphaposposteriorp > 0.5", class = NULL)
hypothesis(alpha_r_phi_07, "rescor__truealphaposp__alphaposposteriorp > 0.5", class = NULL)
hypothesis(alpha_r_phi_09, "rescor__truealphaposp__alphaposposteriorp > 0.5", class = NULL)
```

# Alpha_p
```{r}
# Update data for interactions
# Over alpha_r
alpha_p_alpha_r_01 <- update(alpha_neg_cor, newdata = fit_summary[fit_summary$true_alpha_pos_p == 0.1, ], seed = 1)
alpha_p_alpha_r_03 <- update(alpha_neg_cor, newdata = fit_summary[fit_summary$true_alpha_pos_p == 0.3, ], seed = 1)
alpha_p_alpha_r_05 <- update(alpha_neg_cor, newdata = fit_summary[fit_summary$true_alpha_pos_p == 0.5, ], seed = 1)
alpha_p_alpha_r_07 <- update(alpha_neg_cor, newdata = fit_summary[fit_summary$true_alpha_pos_p == 0.7, ], seed = 1)
alpha_p_alpha_r_09 <- update(alpha_neg_cor, newdata = fit_summary[fit_summary$true_alpha_pos_p == 0.9, ], seed = 1)
# Over phi
alpha_p_phi_01 <- update(alpha_neg_cor, newdata = fit_summary[fit_summary$true_f_p == 0.1, ], seed = 1)
alpha_p_phi_03 <- update(alpha_neg_cor, newdata = fit_summary[fit_summary$true_f_p == 0.3, ], seed = 1)
alpha_p_phi_05 <- update(alpha_neg_cor, newdata = fit_summary[fit_summary$true_f_p == 0.5, ], seed = 1)
alpha_p_phi_07 <- update(alpha_neg_cor, newdata = fit_summary[fit_summary$true_f_p == 0.7, ], seed = 1)
alpha_p_phi_09 <- update(alpha_neg_cor, newdata = fit_summary[fit_summary$true_f_p == 0.9, ], seed = 1)


# Summary
# Over alpha_r
summary(alpha_p_alpha_r_01)
summary(alpha_p_alpha_r_03)
summary(alpha_p_alpha_r_05)
summary(alpha_p_alpha_r_07)
summary(alpha_p_alpha_r_09)
# Over phi
summary(alpha_p_phi_01)
summary(alpha_p_phi_03)
summary(alpha_p_phi_05)
summary(alpha_p_phi_07)
summary(alpha_p_phi_09)


# Test hypotheses
# Over alpha_r
hypothesis(alpha_p_alpha_r_01, "rescor__truealphanegp__alphanegposteriorp > 0.5", class = NULL)
hypothesis(alpha_p_alpha_r_03, "rescor__truealphanegp__alphanegposteriorp > 0.5", class = NULL)
hypothesis(alpha_p_alpha_r_05, "rescor__truealphanegp__alphanegposteriorp > 0.5", class = NULL)
hypothesis(alpha_p_alpha_r_07, "rescor__truealphanegp__alphanegposteriorp > 0.5", class = NULL)
hypothesis(alpha_p_alpha_r_09, "rescor__truealphanegp__alphanegposteriorp > 0.5", class = NULL)

# Over phi
hypothesis(alpha_p_phi_01, "rescor__truealphanegp__alphanegposteriorp > 0.5", class = NULL)
hypothesis(alpha_p_phi_03, "rescor__truealphanegp__alphanegposteriorp > 0.5", class = NULL)
hypothesis(alpha_p_phi_05, "rescor__truealphanegp__alphanegposteriorp > 0.5", class = NULL)
hypothesis(alpha_p_phi_07, "rescor__truealphanegp__alphanegposteriorp > 0.5", class = NULL)
hypothesis(alpha_p_phi_09, "rescor__truealphanegp__alphanegposteriorp > 0.5", class = NULL)
```

# Phi
```{r}
# Update data for interactions
# Over alpha_r
phi_alpha_r_01 <- update(f_cor, newdata = fit_summary[fit_summary$true_alpha_pos_p == 0.1, ], seed = 1)
phi_alpha_r_03 <- update(f_cor, newdata = fit_summary[fit_summary$true_alpha_pos_p == 0.3, ], seed = 1)
phi_alpha_r_05 <- update(f_cor, newdata = fit_summary[fit_summary$true_alpha_pos_p == 0.5, ], seed = 1)
phi_alpha_r_07 <- update(f_cor, newdata = fit_summary[fit_summary$true_alpha_pos_p == 0.7, ], seed = 1)
phi_alpha_r_09 <- update(f_cor, newdata = fit_summary[fit_summary$true_alpha_pos_p == 0.9, ], seed = 1)
# Over alpha_p
phi_alpha_p_01 <- update(f_cor, newdata = fit_summary[fit_summary$true_alpha_neg_p == 0.1, ], seed = 1)
phi_alpha_p_03 <- update(f_cor, newdata = fit_summary[fit_summary$true_alpha_neg_p == 0.3, ], seed = 1)
phi_alpha_p_05 <- update(f_cor, newdata = fit_summary[fit_summary$true_alpha_neg_p == 0.5, ], seed = 1)
phi_alpha_p_07 <- update(f_cor, newdata = fit_summary[fit_summary$true_alpha_neg_p == 0.7, ], seed = 1)
phi_alpha_p_09 <- update(f_cor, newdata = fit_summary[fit_summary$true_alpha_neg_p == 0.9, ], seed = 1)


# Summary
# Over alpha_r
summary(phi_alpha_r_01)
summary(phi_alpha_r_03)
summary(phi_alpha_r_05)
summary(phi_alpha_r_07)
summary(phi_alpha_r_09)
# Over alpha_p
summary(phi_alpha_p_01)
summary(phi_alpha_p_03)
summary(phi_alpha_p_05)
summary(phi_alpha_p_07)
summary(phi_alpha_p_09)


# Test hypotheses
# Over alpha_r
hypothesis(phi_alpha_r_01, "rescor__truefp__fposteriorp > 0.5", class = NULL)
hypothesis(phi_alpha_r_03, "rescor__truefp__fposteriorp > 0.5", class = NULL)
hypothesis(phi_alpha_r_05, "rescor__truefp__fposteriorp > 0.5", class = NULL)
hypothesis(phi_alpha_r_07, "rescor__truefp__fposteriorp > 0.5", class = NULL)
hypothesis(phi_alpha_r_09, "rescor__truefp__fposteriorp > 0.5", class = NULL)

# Over alpha_p
hypothesis(phi_alpha_p_01, "rescor__truefp__fposteriorp > 0.5", class = NULL)
hypothesis(phi_alpha_p_03, "rescor__truefp__fposteriorp > 0.5", class = NULL)
hypothesis(phi_alpha_p_05, "rescor__truefp__fposteriorp > 0.5", class = NULL)
hypothesis(phi_alpha_p_07, "rescor__truefp__fposteriorp > 0.5", class = NULL)
hypothesis(phi_alpha_p_09, "rescor__truefp__fposteriorp > 0.5", class = NULL)
```
