# Parameter recovery Talwar cafRL (T-cafRL)

# Load packages and functions
```{r}
# Load packages
pacman::p_load(ggplot2, tidyverse, RColorBrewer, brms)
options(dplyr.summarise.inform = FALSE)

# Set to source file location 
setwd(dirname(rstudioapi::getActiveDocumentContext()$path))
source("../../utils/quality_check_functions.R")
```

# Load data
```{r}
# Reset and specify model
fit_all = NULL
sim_data = "talwar_cafRL"

# Load data saved in csv
fit_all <- read_csv(paste0("output/", sim_data, "/fit_all.csv"))

# Load data anew
param_combination = readRDS(paste0("../fitting/output/sim_", sim_data, "/param_combination.rds"))

for (i in 1:nrow(param_combination[param_combination$n_agent == 1,])){ # loading for n_agent = 1
 
  fit = as.data.frame(readRDS(paste0("../fitting/output/sim_", sim_data, "/model_talwar_cafRL_fixedbeta/fit_", i, ".rds")))
  fit$model = "talwar_cafRL"
  
  fit = fit[,1:10] # subset relevant columns
  fit$id = i
  fit$n_agent = param_combination$n_agent[i]
  fit$true_alpha_p = param_combination$alpha[i]
  fit$true_alpha_log = brms::logit_scaled(param_combination$alpha[i])
  fit$true_beta = param_combination$beta[i]
  fit$true_theta0_p = brms::inv_logit_scaled(param_combination$theta0[i])
  fit$true_theta0_log = param_combination$theta0[i]
  
  if (exists("fit_all")) {fit_all = rbind(fit_all, fit)} 
  else {fit_all = fit}
}

# Save csv
write_csv(fit_all, "output/talwar_cafRL/fit_all.csv")

# Summarise data
fit_summary = fit_all %>% 
    group_by(id, true_alpha_p, true_beta, true_theta0_p) %>% 
    summarise(true_alpha_log = mean(true_alpha_log),
              true_beta = mean(true_beta),
              true_theta0_log = mean(true_theta0_log),
              alpha_posterior_log = mean(alpha_posterior_log),
              alpha_posterior_p = mean(alpha_posterior_p),
              theta0_posterior_log = mean(theta0_posterior_log),
              theta0_posterior_p = mean(theta0_posterior_p))
              

# Round values
fit_round <- data.frame(lapply(fit_summary, function(x) if(is.numeric(x)) round(x, 2) else x))
```


### Visualisations
To change between plots on the probability scale and the log-odds scale when relevant, change the subscript of the given variable between _p and _log.

## Overall plots for each parameter in the model
```{r}
# Alpha
recovery_overall(fit_round, "true_alpha_p", "alpha_posterior_p", "Alpha", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/overall_alpha.png"), width = 4.2, height = 5)
# Theta_0
recovery_overall(fit_round, "true_theta0_log", "theta0_posterior_log", "Theta_0", y_labs = c(-2.2, -0.85, 0, 0.85, 2.2))
ggsave(paste0("output/", sim_data, "/overall_theta0.png"), width = 4.2, height = 5)
```

## Interactions

# Recovering alpha
```{r}
# Over beta
recovery_over_var_3(fit_round, "true_alpha_p", "alpha_posterior_p", "true_beta", "Beta", "Alpha", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/alpha_beta.png"), width = 4.2, height = 5)
# Over theta_0
recovery_over_var_3(fit_round, "true_alpha_p", "alpha_posterior_p", "true_theta0_log", "Theta_0", "Alpha", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/alpha_theta_0.png"), width = 4.2, height = 5)
```

# Recovering theta_0
```{r}
# Over alpha
recovery_over_var_3(fit_round, "true_theta0_log", "theta0_posterior_log", "true_alpha_p", "Alpha", "Theta_0", y_labs = c(-2.2, -0.85, 0, 0.85, 2.2))
ggsave(paste0("output/", sim_data, "/theta_0_alpha.png"), width = 4.2, height = 5)
# Over beta
recovery_over_var_3(fit_round, "true_theta0_log", "theta0_posterior_log", "true_beta", "Beta", "Theta_0", y_labs = c(-2.2, -0.85, 0, 0.85, 2.2))
ggsave(paste0("output/", sim_data, "/theta_0_beta.png"), width = 4.2, height = 5)
```


### Correlations
Allows us to get the correlations as part of the "residual correlations"

## Overall correlations
```{r}
# Formulas
f_alpha <- bf(mvbind(true_alpha_p, alpha_posterior_p) ~ 1) + set_rescor(TRUE)
f_theta_0 <- bf(mvbind(true_theta0_log, theta0_posterior_log) ~ 1) + set_rescor(TRUE)

# Run models
alpha_cor <- brm(
  formula = f_alpha,
  data = fit_summary,
  family = gaussian,
  chains = 4,
  cores = 4,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 20),
  seed = 1)

theta_0_cor <- brm(
  formula = f_theta_0,
  data = fit_summary,
  family = gaussian,
  chains = 4,
  cores = 4,
  control = list(adapt_delta = 0.99,
                 max_treedepth = 20),
  seed = 1)

# Summary
summary(alpha_cor)
summary(theta_0_cor)

# Get parameter/variable names
variables(alpha_cor)
variables(theta_0_cor)

# Test hypotheses
hypothesis(alpha_cor, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(theta_0_cor, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
```

## Interactions

# Alpha
```{r}
# Update data for interactions
# Over beta
alpha_beta_01 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_beta == 0.1, ], seed = 1)
alpha_beta_05 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_beta == 0.5, ], seed = 1)
alpha_beta_1 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_beta == 1, ], seed = 1)
alpha_beta_2 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_beta == 2, ], seed = 1)
alpha_beta_3 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_beta == 3, ], seed = 1)
alpha_beta_5 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_beta == 5, ], seed = 1)
alpha_beta_10 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_beta == 10, ], seed = 1)
# Over theta_0
alpha_theta_0_01 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_theta0_log < -2, ], seed = 1)
alpha_theta_0_03 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_theta0_log < -0.5 & fit_summary$true_theta0_log > -1, ], seed = 1)
alpha_theta_0_05 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_theta0_log == 0, ], seed = 1)
alpha_theta_0_07 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_theta0_log > 0.5 & fit_summary$true_theta0_log < 1, ], seed = 1)
alpha_theta_0_09 <- update(alpha_cor, newdata = fit_summary[fit_summary$true_theta0_log > 2, ], seed = 1)

# Summary
# Over beta
summary(alpha_beta_01)$rescor_pars
summary(alpha_beta_05)$rescor_pars
summary(alpha_beta_1)$rescor_pars
summary(alpha_beta_2)$rescor_pars
summary(alpha_beta_3)$rescor_pars
summary(alpha_beta_5)$rescor_pars
summary(alpha_beta_10)$rescor_pars
# Over theta_0
summary(alpha_theta_0_01)
summary(alpha_theta_0_03)
summary(alpha_theta_0_05)
summary(alpha_theta_0_07)
summary(alpha_theta_0_09)


# Test hypotheses
# Over beta
hypothesis(alpha_beta_01, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(alpha_beta_05, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(alpha_beta_1, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(alpha_beta_2, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(alpha_beta_3, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(alpha_beta_5, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(alpha_beta_10, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
# Over theta_0
hypothesis(alpha_theta_0_01, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(alpha_theta_0_03, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(alpha_theta_0_05, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(alpha_theta_0_07, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(alpha_theta_0_09, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
```

# Theta_0
```{r}
# Update data for interactions
# Over alpha
theta_0_alpha_01 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_alpha_p == 0.1, ], seed = 1)
theta_0_alpha_03 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_alpha_p == 0.3, ], seed = 1)
theta_0_alpha_05 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_alpha_p == 0.5, ], seed = 1)
theta_0_alpha_07 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_alpha_p == 0.7, ], seed = 1)
theta_0_alpha_09 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_alpha_p == 0.9, ], seed = 1)
# Over beta
theta_0_beta_01 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_beta == 0.1, ], seed = 1)
theta_0_beta_05 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_beta == 0.5, ], seed = 1)
theta_0_beta_1 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_beta == 1, ], seed = 1)
theta_0_beta_2 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_beta == 2, ], seed = 1)
theta_0_beta_3 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_beta == 3, ], seed = 1)
theta_0_beta_5 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_beta == 5, ], seed = 1)
theta_0_beta_10 <- update(theta_0_cor, newdata = fit_summary[fit_summary$true_beta == 10, ], seed = 1)


# Summary
# Over alpha
summary(theta_0_alpha_01)
summary(theta_0_alpha_03)
summary(theta_0_alpha_05)
summary(theta_0_alpha_07)
summary(theta_0_alpha_09)
# Over beta
summary(theta_0_beta_01)
summary(theta_0_beta_05)
summary(theta_0_beta_1)
summary(theta_0_beta_2)
summary(theta_0_beta_3)
summary(theta_0_beta_5)
summary(theta_0_beta_10)


# Test hypotheses
# Over alpha
hypothesis(theta_0_alpha_01, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
hypothesis(theta_0_alpha_03, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
hypothesis(theta_0_alpha_05, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
hypothesis(theta_0_alpha_07, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
hypothesis(theta_0_alpha_09, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
# Over beta
hypothesis(theta_0_beta_01, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
hypothesis(theta_0_beta_05, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
hypothesis(theta_0_beta_1, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
hypothesis(theta_0_beta_2, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
hypothesis(theta_0_beta_3, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
hypothesis(theta_0_beta_5, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
hypothesis(theta_0_beta_10, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)
```


### BETA SUBSET
Running the above on subsets of data only including beta-values which led to correlations >= 0.5 and high evidence to inspect how that affects the recovery of the parameters.

```{r}
# Subset for plots and correlations

# Alpha subset
fit_round_alpha <- fit_round %>% filter(true_beta >= 0.5 & true_beta <= 3)
fit_summary_alpha <- fit_summary %>% filter(true_beta >= 0.5 & true_beta <= 3)

# Theta_0 subset
fit_round_theta_0 <- fit_round %>% filter(true_beta >= 1 & true_beta <= 5)
fit_summary_theta_0 <- fit_summary %>% filter(true_beta >= 1 & true_beta <= 5)
```

### Visualisations
To change between plots on the probability scale and the log-odds scale when relevant, change the subscript of the given variable between _p and _log.

## Overall plots for each parameter in the model
```{r}
# Alpha
recovery_overall(fit_round_alpha, "true_alpha_p", "alpha_posterior_p", "Alpha", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/sub/overall_alpha_sub.png"), width = 4.2, height = 5)
# Theta_0
recovery_overall(fit_round_theta_0, "true_theta0_log", "theta0_posterior_log", "Theta_0", y_labs = c(-2.2, -0.85, 0, 0.85, 2.2))
ggsave(paste0("output/", sim_data, "/sub/overall_theta0_sub.png"), width = 4.2, height = 5)
```

## Interactions

# Recovering alpha
```{r}
# Over beta
recovery_over_var_3(fit_round_alpha, "true_alpha_p", "alpha_posterior_p", "true_beta", "Beta", "Alpha", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/sub/alpha_beta_sub.png"), width = 4.2, height = 5)
# Over theta0
recovery_over_var_3(fit_round_alpha, "true_alpha_p", "alpha_posterior_p", "true_theta0_log", "Theta_0", "Alpha", y_labs = c(0.1, 0.3, 0.5, 0.7, 0.9))
ggsave(paste0("output/", sim_data, "/sub/alpha_theta_0_sub.png"), width = 4.2, height = 5)
```

# Recovering theta_0
```{r}
# Over alpha
recovery_over_var_3(fit_round_theta_0, "true_theta0_log", "theta0_posterior_log", "true_alpha_p", "Alpha", "Theta_0", y_labs = c(-2.2, -0.85, 0, 0.85, 2.2))
ggsave(paste0("output/", sim_data, "/sub/theta_0_alpha_sub.png"), width = 4.2, height = 5)
# Over beta
recovery_over_var_3(fit_round_theta_0, "true_theta0_log", "theta0_posterior_log", "true_beta", "Beta", "Theta_0", y_labs = c(-2.2, -0.85, 0, 0.85, 2.2))
ggsave(paste0("output/", sim_data, "/sub/theta_0_beta_sub.png"), width = 4.2, height = 5)
```


### Correlations
Allows us to get the correlations as part of the "residual correlations"

## Overall correlations
```{r}
# Run models on subsets of data
alpha_cor_sub <- update(alpha_cor, newdata = fit_summary_alpha, seed = 1)
theta_0_cor_sub <- update(theta_0_cor, newdata = fit_summary_theta_0, seed = 1)

# Summary
summary(alpha_cor_sub)
summary(theta_0_cor_sub)

# Get parameter/variable names
variables(alpha_cor_sub)
variables(theta_0_cor_sub)

# Test hypotheses
hypothesis(alpha_cor_sub, "rescor__truealphap__alphaposteriorp > 0.5", class = NULL)
hypothesis(theta_0_cor_sub, "rescor__truetheta0log__theta0posteriorlog > 0.5", class = NULL)

```

