
## Load packages and functions, etc.
```{r}
# Load packages
pacman::p_load(comprehenr, purrr, tidyverse)

# Suppress messages for group_by
options(dplyr.summarise.inform = FALSE)

# Load functions
dirname(rstudioapi::getActiveDocumentContext()$path)
source("simulation_functions_yearsley.R")
```


## Replicate figures from Yearsely et al. (2021)

To simulate data with the run_simulation function, specify the following parameters:
* group: group name for the simulated subjects
* n_correct: criterion of correct trials for moving to next stage

* f: dimension shift parameter/attention switching parameter (0-1)
* r: reward learning rate (0-1)
* p: punishment learning rate (0-1)
* d: decision consistency (-inf to + inf)
* lambda: disengagement/focus parameter (0-1)
* switch1: continuation parameter (0-1)
* switch2: continuation parameter (0-1)

### FIGURE 2 PLOTS ###
```{r}
# Define parameters
control_params = list(
  group = "control",
  n_correct = 6,
  f = 0.4,
  r = 0.5,
  p = 0.5,
  d = 3,
  lambda = 0.05,
  switch1 = 0.95,
  switch2 = 0.95
)
  
reduced_f_params = list(
  group = "reduced_f",
  n_correct = 6,
  f = 0.1,
  r = 0.5,
  p = 0.5,
  d = 3,
  lambda = 0.05,
  switch1 = 0.95,
  switch2 = 0.95
  
)

# Run simulation with the parameters specified above for n agents with the given seed
control_df = run_simulation(control_params, 1000, seq(1,1000))
reduced_f_df = run_simulation(reduced_f_params, 1000, seq(1,1000))
# Combine data for plot of both groups
combined = rbind(control_df, reduced_f_df)

# Define stage names for plot
combined$stage_name = ifelse(combined$stage == 1, "1: SD",
                        ifelse(combined$stage == 2, "2: SDr",
                        ifelse(combined$stage == 3, "3: C-D",
                        ifelse(combined$stage == 4, "4: CD",
                        ifelse(combined$stage == 5, "5: CDr",
                        ifelse(combined$stage == 6, "6: ID",
                        ifelse(combined$stage == 7, "7: IDr",
                        ifelse(combined$stage == 8, "8: ED",
                        ifelse(combined$stage == 9, "9: EDr", NA)))))))))

# Measures
# Attrition rate
attrition = combined %>% filter(stage_completed == 1) %>% 
  group_by(group, stage, stage_name) %>% 
  summarise(attrition_rate = length(unique(agent))/1000)

# Errors to criterion
errors = combined %>% 
  group_by(group, agent, stage, stage_name) %>%
  summarise(error_to_criterion_agent = sum(choice == 0)) %>% 
  group_by(group, stage, stage_name) %>% 
  summarise(error_to_criterion = mean(error_to_criterion_agent))

# Trials to criterion
trials = combined %>% 
  group_by(group, agent, stage, stage_name) %>%
  summarise(trial_to_criterion_agent = max(trial)) %>% 
  group_by(group, stage, stage_name) %>% 
  summarise(trial_to_criterion = mean(trial_to_criterion_agent))


# Plots
# Attrition rate
ggplot(attrition, aes(x = stage_name, y = attrition_rate, color = group, group = group)) + 
  geom_line() + 
  geom_point() + 
  scale_color_manual(values = c("control" = "red", "reduced_f" = "blue")) +
  scale_y_continuous(n.breaks = 10, limits = c(0,1)) +
  ylab("Percent Completing") +
  xlab("Stage") +
  ggtitle("Attrition Rate") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
#ggsave(paste0("simulation_figures/fig2_attrition.png"), width = 4, height = 5.5)


# Errors to criterion
ggplot(errors, aes(x = stage_name, y = error_to_criterion, color = group, group = group)) + 
  geom_line() + 
  geom_point() + 
  scale_color_manual(values = c("control" = "red", "reduced_f" = "blue")) +
  scale_y_continuous(n.breaks = 11, limits = c(0,10)) +
  ylab("Errors to Criterion") +
  xlab("Stage") +
  ggtitle("Errors") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
#ggsave(paste0("simulation_figures/fig2_errors.png"), width = 4, height = 5.5)
  

# Trials to criterion
ggplot(trials, aes(x = stage_name, y = trial_to_criterion, color = group, group = group)) + 
  geom_line() + 
  geom_point() + 
  scale_color_manual(values = c("control" = "red", "reduced_f" = "blue")) +
  scale_y_continuous(n.breaks = 7, limits = c(0,31)) +
  ylab("Trials to Criterion") +
  xlab("Stage") +
  ggtitle("Trials") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
#ggsave(paste0("simulation_figures/fig2_trials.png"), width = 4, height = 5.5)

```

### FIGURE 3 PLOTS ###
```{r}
# Define paramters
low_f_params = list(
  group = "low_f",
  n_correct = 6,
  f = 0.1,
  r = 0.15,
  p = 0.15,
  d = 3,
  lambda = 0.05,
  switch1 = 0.95,
  switch2 = 0.95
)
  
high_f_params = list(
  group = "high_f",
  n_correct = 6,
  f = 1,
  r = 0.15,
  p = 0.15,
  d = 3,
  lambda = 0.05,
  switch1 = 0.95,
  switch2 = 0.95
  
)

# Run simulation with the parameters specified above for n agents with the given seed
low_f_df = run_simulation(low_f_params, 1000, seq(1,1000))
high_f_df = run_simulation(high_f_params, 1000, seq(1,1000))
# Combine data for plot of both groups
combined = rbind(low_f_df, high_f_df)

# Define stage names for plot
combined$stage_name = ifelse(combined$stage == 1, "1: SD",
                        ifelse(combined$stage == 2, "2: SDr",
                        ifelse(combined$stage == 3, "3: C-D",
                        ifelse(combined$stage == 4, "4: CD",
                        ifelse(combined$stage == 5, "5: CDr",
                        ifelse(combined$stage == 6, "6: ID",
                        ifelse(combined$stage == 7, "7: IDr",
                        ifelse(combined$stage == 8, "8: ED",
                        ifelse(combined$stage == 9, "9: EDr", NA)))))))))

# Measures
# Attrition Rate
attrition = combined %>% filter(stage_completed == 1) %>% 
  group_by(group, stage, stage_name) %>% 
  summarise(attrition_rate = length(unique(agent))/1000)

# Errors to criterion
errors = combined %>% 
  group_by(group, agent, stage, stage_name) %>%
  summarise(error_to_criterion_agent = sum(choice == 0)) %>% 
  group_by(group, stage, stage_name) %>% 
  summarise(error_to_criterion = mean(error_to_criterion_agent))

# Trials to criterion
trials = combined %>% 
  group_by(group, agent, stage, stage_name) %>%
  summarise(trial_to_criterion_agent = max(trial)) %>% 
  group_by(group, stage, stage_name) %>% 
  summarise(trial_to_criterion = mean(trial_to_criterion_agent))


# Plots
# Attrition rate
ggplot(attrition, aes(x = stage_name, y = attrition_rate, color = group, group = group)) + 
  geom_line() + 
  geom_point() + 
  scale_color_manual(values = c("low_f" = "red", "high_f" = "blue")) +
  scale_y_continuous(n.breaks = 10, limits = c(0,1)) +
  ylab("Percent Completing") +
  xlab("Stage") +
  ggtitle("Attrition Rate") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
ggsave(paste0("simulation_figures/fig3_attrition.png"), width = 4, height = 5.5)

# Errors to criterion
ggplot(errors, aes(x = stage_name, y = error_to_criterion, color = group, group = group)) + 
  geom_line() + 
  geom_point() + 
  scale_color_manual(values = c("low_f" = "red", "high_f" = "blue")) +
  scale_y_continuous(n.breaks = 11, limits = c(0,16)) +
  ylab("Errors to Criterion") +
  xlab("Stage") +
  ggtitle("Errors") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
ggsave(paste0("simulation_figures/fig3_errors.png"), width = 4, height = 5.5)
  

# Trials to criterion
ggplot(trials, aes(x = stage_name, y = trial_to_criterion, color = group, group = group)) + 
  geom_line() + 
  geom_point() + 
  scale_color_manual(values = c("low_f" = "red", "high_f" = "blue")) +
  scale_y_continuous(n.breaks = 7, limits = c(0,35)) +
  ylab("Trials to Criterion") +
  xlab("Stage") +
  ggtitle("Trials") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
ggsave(paste0("simulation_figures/fig3_trials.png"), width = 4, height = 5.5)
```

### FIGURE 4 PLOTS ###
```{r}
# Define parameters
low_f_moderate_p_params = list(
  group = "low_f_moderate_p",
  n_correct = 6,
  f = 0.08,
  r = 0.3,
  p = 0.3,
  d = 3,
  lambda = 0.05,
  switch1 = 0.95,
  switch2 = 0.95
)
  
moderate_f_low_p_params = list(
  group = "moderate_f_low_p",
  n_correct = 6,
  f = 0.3,
  r = 0.3,
  p = 0.08,
  d = 3,
  lambda = 0.05,
  switch1 = 0.95,
  switch2 = 0.95
  
)

# Run simulation with the parameters specified above for n agents with the given seed
low_f_moderate_p_df = run_simulation(low_f_moderate_p_params, 1000, seq(1,1000))
moderate_f_low_p_df = run_simulation(moderate_f_low_p_params, 1000, seq(1,1000))
# Combine data for plot of both groups
combined = rbind(low_f_moderate_p_df, moderate_f_low_p_df)

# Define stage names for plot
combined$stage_name = ifelse(combined$stage == 1, "1: SD",
                        ifelse(combined$stage == 2, "2: SDr",
                        ifelse(combined$stage == 3, "3: C-D",
                        ifelse(combined$stage == 4, "4: CD",
                        ifelse(combined$stage == 5, "5: CDr",
                        ifelse(combined$stage == 6, "6: ID",
                        ifelse(combined$stage == 7, "7: IDr",
                        ifelse(combined$stage == 8, "8: ED",
                        ifelse(combined$stage == 9, "9: EDr", NA)))))))))

# Measures
# Attrition Rate
attrition = combined %>% filter(stage_completed == 1) %>% 
  group_by(group, stage, stage_name) %>% 
  summarise(attrition_rate = length(unique(agent))/1000)

# Errors to criterion
errors = combined %>% 
  group_by(group, agent, stage, stage_name) %>%
  summarise(error_to_criterion_agent = sum(choice == 0)) %>% 
  group_by(group, stage, stage_name) %>% 
  summarise(error_to_criterion = mean(error_to_criterion_agent))

# Trials to criterion
trials = combined %>% 
  group_by(group, agent, stage, stage_name) %>%
  summarise(trial_to_criterion_agent = max(trial)) %>% 
  group_by(group, stage, stage_name) %>% 
  summarise(trial_to_criterion = mean(trial_to_criterion_agent))


# Plots
# Attrition rate
ggplot(attrition, aes(x = stage_name, y = attrition_rate, color = group, group = group)) + 
  geom_line() + 
  geom_point() + 
  scale_color_manual(values = c("low_f_moderate_p" = "red", "moderate_f_low_p" = "blue")) +
  scale_y_continuous(n.breaks = 10, limits = c(0,1)) +
  ylab("Percent Completing") +
  xlab("Stage") +
  ggtitle("Attrition Rate") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
ggsave(paste0("simulation_figures/fig4_attrition.png"), width = 4, height = 5.5)

# Errors to criterion
ggplot(errors, aes(x = stage_name, y = error_to_criterion, color = group, group = group)) + 
  geom_line() + 
  geom_point() + 
  scale_color_manual(values = c("low_f_moderate_p" = "red", "moderate_f_low_p" = "blue")) +
  scale_y_continuous(n.breaks = 11, limits = c(0,15.3)) +
  ylab("Errors to Criterion") +
  xlab("Stage") +
  ggtitle("Errors") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
ggsave(paste0("simulation_figures/fig4_errors.png"), width = 4, height = 5.5)
  

# Trials to criterion
ggplot(trials, aes(x = stage_name, y = trial_to_criterion, color = group, group = group)) + 
  geom_line() + 
  geom_point() + 
  scale_color_manual(values = c("low_f_moderate_p" = "red", "moderate_f_low_p" = "blue")) +
  scale_y_continuous(n.breaks = 7, limits = c(0,35)) +
  ylab("Trials to Criterion") +
  xlab("Stage") +
  ggtitle("Trials") +
  theme_bw() +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "none")
ggsave(paste0("simulation_figures/fig4_trials.png"), width = 4, height = 5.5)
```

