
# Loading packages and functions, etc.
```{r}
# Load packages
pacman::p_load(tidyverse, random, brms)

# Suppress messages for group_by
options(dplyr.summarise.inform = FALSE)

# Load simulation functions
dirname(rstudioapi::getActiveDocumentContext()$path)
source("simulation_functions_talwar.R")
```

To simulate data with the run_simulation function, specify the following parameters:
* Model: which model ("frl" or "cafrl")
* group: group name for the simulated subjects
* n_correct: criterion of correct trials for moving to next stage

* alpha: generic learning rate (0-1)
* beta: inverse temperature (0-inf)
* theta_init: initial dimension weight (-inf to +inf). Only relevant in the cafRL.
* epsilon: not relevant for fRL and the cafRL models implemented in this script

# Model 1:Feature RL
```{r}
# Explore output of different values for the simulation
params = list(
  model = "fRL",
  group = "test",
  n_correct = 6,
  alpha = 0.1, 
  beta = 3,
  theta_init = NA,
  epsilon = NA)

# Run simulation with the parameters specified above for n agents with the given seed
output_fRL = run_simulation(params, 1, 1)



# Replication of plots in Talwar et al. (2021)
params = list(
  model = "fRL",
  group = "plots",
  n_correct = 6,
  alpha = 0.62, 
  beta = 0.91,
  theta_init = NA,
  epsilon = NA)

# Run simulation with specified parameters for 500 agents with seeds from 1-500
plot_fRL = run_simulation(params, 500, seq(1,500))

# Get number of errors
errors_fRL = plot_fRL %>% 
  group_by(group, agent, stage) %>%
  summarise(error_to_criterion_agent = sum(choice == 0))

# Define stage names for plot
errors_fRL$stage_name = ifelse(errors_fRL$stage == 1, "1: SD",
                        ifelse(errors_fRL$stage == 2, "2: SDr",
                        ifelse(errors_fRL$stage == 3, "3: C-D",
                        ifelse(errors_fRL$stage == 4, "4: CD",
                        ifelse(errors_fRL$stage == 5, "5: CDr",
                        ifelse(errors_fRL$stage == 6, "6: ID",
                        ifelse(errors_fRL$stage == 7, "7: IDr",
                        ifelse(errors_fRL$stage == 8, "8: ED",
                        ifelse(errors_fRL$stage == 9, "9: EDr", NA)))))))))

# Plot
ggplot(errors_fRL, aes(x = stage_name, y = error_to_criterion_agent)) + 
  geom_jitter(width = 0.2, size = 0.4, colour = "#9fb1dd") +
  labs(title ="Replication of error plot for fRL-model") +
  ylab("Errors") +
  xlab("Stage") +
  ylim(-1,20) + 
  theme_bw() 

# Save plot
#ggsave("simulation_figures/fRL_error_plot1.png", width = 6, height = 4)
```

# Model 2: Combined Attention-Modulated Feature RL
```{r}
# Explore output of different values for the simulation
params = list(
  model = "cafRL",
  group = "test",
  n_correct = 6,
  alpha = 0.1, 
  beta = 3,
  theta_init = 1,
  epsilon = NA)

# Run simulation with the parameters specified above for n agents with the given seed
test_output_cafRL = run_simulation(params, 1, 1)



# Replication of plots in Talwar et al. (2021)
params = list(
  model = "cafRL",
  group = "plots",
  n_correct = 6,
  alpha = 0.92, 
  beta = 1.34,
  theta_init = 1.78,
  epsilon = NA)

# Run simulation with specified parameters for 500 agents with seeds from 1-500
plot_cafRL = run_simulation(params, 500, seq(1,500))

# Get number of errors
errors_cafRL = plot_cafRL %>% 
  group_by(group, agent, stage) %>%
  summarise(error_to_criterion_agent = sum(choice == 0))

# Define stage names for plot
errors_cafRL$stage_name = ifelse(errors_cafRL$stage == 1, "1: SD",
                          ifelse(errors_cafRL$stage == 2, "2: SDr",
                          ifelse(errors_cafRL$stage == 3, "3: C-D",
                          ifelse(errors_cafRL$stage == 4, "4: CD",
                          ifelse(errors_cafRL$stage == 5, "5: CDr",
                          ifelse(errors_cafRL$stage == 6, "6: ID",
                          ifelse(errors_cafRL$stage == 7, "7: IDr",
                          ifelse(errors_cafRL$stage == 8, "8: ED",
                          ifelse(errors_cafRL$stage == 9, "9: EDr", NA)))))))))

# Plot
ggplot(errors_cafRL, aes(x = stage_name, y = error_to_criterion_agent)) + 
  geom_jitter(width = 0.2, size = 0.4, colour = "#6b86c8") +
  labs(title ="Replication of error plot for cafRL-model") +
  ylab("Errors") +
  xlab("Stage") +
  theme_bw()

#ggsave("simulation_figures/cafRL_error_plot1.png", width = 6, height = 4)
```

